Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-02-23 Submission_2016_source/submission.tex
Update submission.tex

STPV, ST, and TPV systems all share common surfaces but operate under different conditions.  ST and STPV systems offer an alternative to PV power generation in alternative energy systems.  Since both are heat engines, they do not adhere to the Shockley-Queisser limit and can theoretically exhibit extremely high efficiencies.  Additionally, since both ST and STPV systems rely on elements heated to high temperatures via concentrated solar energy, they are easy to modify for thermal storage of energy.  This would allow them to operate into the night.  An advantage of ST systems over STPV systems is that ST systems do not require the use of PV cells.  The PV cells in STPV systems are expensive and can limit overall system size.  Conversely, an advantage of STPV systems over ST systems is that STPV systems have no thermal fluid or moving parts.  This leads to them being more stable and compact solutions.  Overall, ST tends to lend itself to large, immobile power installations while STPV is better suited for small applications.  TPV systems operate on the same principle as STPV systems, but rely on an external heat source instead of solar energy.  This allows them to be used in energy reclamation systems.

>>>>

STPV, ST, and TPV systems all share common surfaces but operate under different conditions.  ST and STPV systems offer an alternative to PV power generation in alternative energy systems.  Since both are heat engines, they do not adhere to the Shockley-Queisser limit and can theoretically exhibit extremely high efficiencies.  Additionally, since both ST and STPV systems rely on elements heated to high temperatures via concentrated solar energy, they are easy to modify for thermal storage of energy~\cite{Night_time_Performance}.  This would allow them to operate into the night.  An advantage of ST systems over STPV systems is that ST systems do not require the use of PV cells.  The PV cells in STPV systems are expensive and can limit overall system size.  Conversely, an advantage of STPV systems over ST systems is that STPV systems have no thermal fluid or moving parts.  This leads to them being more stable and compact solutions.  Overall, ST tends to lend itself to large, immobile power installations while STPV is better suited for small applications.  TPV systems operate on the same principle as STPV systems, but rely on an external heat source instead of solar energy~\cite{Prototype_TPV}.  This allows them to be used in energy reclamation systems.
